A higher order approximate static condensation method for multi-material diffusion problems

### 2019-01-26 asc.tex
Fix a typo

	Now, when the mappings between local and global approximations of $\lambda$ are defined, we are ready to proceed with the assembly of the global matrix $\vect S_\bmesh$. The flux continuity over the face $F$ \big(condition~\eqref{flux_cont}\big) yields
	\begin{equation}\label{eq:aux1pre}
		\left\{\begin{split}
			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0, \\
			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
		\end{split}\right.
		%\quad\Leftrightarrow \\
		%		\sum_{i \in I_{\mfaces^+_F}} u^{\text{ext}}_{\mmesh^+\,i}\,\Delta s^+_i\,|\mfaces^+_{F\,i}| &+ \sum_{i \in I_{\mfaces^-_F}} u^{\text{ext}}_{\mmesh^-\,i}\,\Delta s^-_i\,|\mfaces^-_{F\,i}| = 0,
	\end{equation}
	or in the matrix form
	\begin{equation}\label{eq:aux1}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_{i+m} + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect u}^{\text{ext}}_{\mmesh^-} \right)_{j+m} = 0, \quad m \in \{0, 1\}
	\end{equation}
	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively. ($m = 0$ corresponds to the first equation in~\eqref{eq:aux1pre} and $m = 1$ corresponds to the second one; further we omit ``$+m$" for simplicity.) For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$. If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have
	\begin{equation*}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i = \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
		{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_k \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell^+),\:k\,\in\,\{0,\,1\}}.
	\end{equation*}

>>>>

	Now, when the mappings between local and global approximations of $\lambda$ are defined, we are ready to proceed with the assembly of the global matrix $\vect S_\bmesh$. The flux continuity over the face $F$ \big(condition~\eqref{flux_cont}\big) yields
	\begin{equation}\label{eq:aux1pre}
		\left\{\begin{split}
			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,|f| &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,|f| &= 0, \\
			\sum_{f\in \mfaces_F(T^+)} u^{\text{ext}}_{\mmesh^+}(f)\,\int_{f} s_1 \diff{l} &+ \sum_{f\in \mfaces_F(T^-)} u^{\text{ext}}_{\mmesh^-}(f)\,\int_{f} s_1 \diff{l} &= 0
		\end{split}\right.
		%\quad\Leftrightarrow \\
		%		\sum_{i \in I_{\mfaces^+_F}} u^{\text{ext}}_{\mmesh^+\,i}\,\Delta s^+_i\,|\mfaces^+_{F\,i}| &+ \sum_{i \in I_{\mfaces^-_F}} u^{\text{ext}}_{\mmesh^-\,i}\,\Delta s^-_i\,|\mfaces^-_{F\,i}| = 0,
	\end{equation}
	or in the matrix form
	\begin{equation}\label{eq:aux1}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_{i+m} + \left( \vect R^T_{\mmesh^-}\,\vect C_{\mmesh^-}\,{\vect u}^{\text{ext}}_{\mmesh^-} \right)_{j+m} = 0, \quad m \in \{0, 1\}
	\end{equation}
	where $i$ and $j$ are the local indexes of the face $F$ in the cells $T^+$ and $T^-$, respectively ($m = 0$ corresponds to the first equation in~\eqref{eq:aux1pre} and $m = 1$ corresponds to the second one; further we omit ``$+m$" for simplicity). For the Neumann part of the boundary of~$\bcell^\pm$ we set $\mfaces_N(\bcell^\pm) \coloneqq \{ f \in \mfaces[ext](\bcell^\pm)\::\:f \subset \partial\Omega_N \}$. If $F$ from $T^+$ belongs to the Neumann part of the boundary, then we have
	\begin{equation*}
		\left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect u}^{\text{ext}}_{\mmesh^+} \right)_i = \left( \vect R^T_{\mmesh^+}\,\vect C_{\mmesh^+}\,{\vect g}_{N\,\mmesh^+} \right)_i, \quad
		{\vect g}_{N\,\mmesh^+} \coloneqq \left\{ \int_f g_N\,s_m \diff{l}\,/\,|f| \right\}_{f\,\in\,\mfaces_N(\bcell^+),\:m\,\in\,\{0,\,1\}}.
	\end{equation*}
